Test parsing of Proff.no table (Kreftforeningen)

### 2022-07-07 Test parsing of Proff table.Rmd
Slightly more robust function added. Added headings. Added html for Rode Kors.

---
title: "Test parsing of Proff.no table (Kreftforeningen)"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-06'
output: html_document
---

@@

@@

Note that we might have to convert implicitly negative numbers.

@@

@@

@@

>>>>

---
title: "Test parsing of Proff.no table (Kreftforeningen)"
author: "Torbjørn Skinnemoen Ottersen"
date: '2022-07-06'
output: 
  html_document: 
    df_print: paged
---

@@

### Reading in stages

@@

>*Note that we might have to convert implicitly negative numbers.*

### Testing with different file

@@

### As a single operation

@@

### Function 1

@@

### Slightly more robust function

- `file`: name and location of html file
- `start`: first available year as a string ("")
- `end`: last available year as a string ("")

```{r function_modified}
read_proff2 <- function(file, start, end){
  read_html(file, encoding = "UTF-8") |> 
  html_node("#inner-frame") |> 
  html_table() |> 
  select(
    REGNSKAPSPERIODE:start) |> 
  mutate(
    REGNSKAPSPERIODE = str_squish(REGNSKAPSPERIODE)
  ) |> 
    filter(
      !row_number() > 176
    ) |>
  filter(
    !grepl("Lukk", REGNSKAPSPERIODE)
    ) |> 
  pivot_longer(
    end:start, names_to = "year") |> 
  mutate(
    value = na_if(value, "-"),
    year = as.integer(year)) |> 
  filter(
    REGNSKAPSPERIODE != "Sluttdato" & REGNSKAPSPERIODE != "Startdato" &
      REGNSKAPSPERIODE != "Valutakode") |> 
  mutate(
    value = str_replace_all(value, "\\s", "")
  ) |> 
  mutate(
    value = as.numeric(value)
  ) |> 
  mutate(
    value = ifelse(grepl("i hele 1000", REGNSKAPSPERIODE), NA, value)
  )
}

read_proff2("Links/Kors.html", "2001", "2020") |> 
  arrange(desc(year))
```
